### 2017-09-09 paper/evaluation.tex
Fixes and added my progress mark

``consumes'' the next test class and spawns a JVM to run it.  Recall
that in our setup (see Section~\ref{sec:setup}), we limited our kernel
to use only three cores and reserved one for OS-related processes.  To
verify that our approach satisfies the purpose of this experiment, we
executed some subjects on Maven and compared the performance with our
artifacts and observed insignificant differences (a fraction of
seconds in most cases).  To assure that our experiments terminate
(recall that deadlock or livelock could occur) we used the
\CodeIn{timeout} command~\cite{timeout-cmd} configured to dispatch a
\emph{kill} signal if test execution exceeds a given time
limit. Finally, we saved each execution log and stack traces generated
from JUnit to collect the execution time, the number of failing tests,
and for reference to analyze and diagnose outliers in our results.

>>>>

``consumes'' the next test class and spawns a JVM to run it.}
Recall that in our setup (see Section~\ref{sec:setup}), we limited our
kernel to use only three cores and reserved one for OS-related
processes.  To assure that our experiments terminate (recall that
deadlock or livelock could occur) we used the \CodeIn{timeout}
command~\cite{timeout-cmd} configured to dispatch a \emph{kill} signal
if test execution exceeds a given time limit. Finally, we saved each
execution log and stack traces generated from JUnit to collect the
execution time, the number of failing tests, and to diagnose outliers
in our results.
